Exploratory Analysis

### 2023-11-30 Code/Draft1Rmd.Rmd
Updated line plot

combined_yearly <- healthrank_to_yearly(health_ranking)

ggplot() +
  geom_line(data = or_yearly, aes(x = year, y = log(combined_overdose_deaths), color = "Oregon")) +
  geom_line(data = ca_yearly, aes(x = year, y = log(combined_overdose_deaths), color = "California")) +
  geom_line(data = wa_yearly, aes(x = year, y = log(combined_overdose_deaths), color = "Washington")) +
  geom_point(data = or_yearly, aes(x = year, y = log(combined_overdose_deaths), color = "Oregon"), size = 1) +
  geom_point(data = ca_yearly, aes(x = year, y = log(combined_overdose_deaths), color = "California"), size = 1) +
  geom_point(data = wa_yearly, aes(x = year, y = log(combined_overdose_deaths), color = "Washington"), size = 1) +
  scale_color_manual(name = "State",
                     values = c("Oregon" = "blue", "California" = "red", "Washington" = "green")) +
  labs(y = "Log Combined Overdose Deaths") +
  theme_bw()
```
```

>>>>

ggplot() +
  geom_line(data = or_yearly, aes(x = year, y = log(combined_overdose_deaths), color = "Oregon")) +
  geom_line(data = ca_yearly, aes(x = year, y = log(combined_overdose_deaths), color = "California")) +
  geom_line(data = wa_yearly, aes(x = year, y = log(combined_overdose_deaths), color = "Washington")) +
  geom_point(data = or_yearly, aes(x = year, y = log(combined_overdose_deaths), color = "Oregon"), size = 3) +
  geom_point(data = ca_yearly, aes(x = year, y = log(combined_overdose_deaths), color = "California"), size = 3) +
  geom_point(data = wa_yearly, aes(x = year, y = log(combined_overdose_deaths), color = "Washington"), size = 3) +
  geom_vline(xintercept = as.numeric("2021"), linetype = "dashed", color = "black", size = 1) +
  scale_color_manual(name = "State",
                     values = c("Oregon" = "blue", "California" = "red", "Washington" = "green")) +
  labs(y = "Log Combined Overdose Deaths") +
  theme_bw()
```
```
